---
title: "greenx workflow"
author: "Beni Stocker"
date: "2/10/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rbeni)
library(patchwork)
library(extRemes)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)

source("R/calc_anom_ndvi.R")
source("R/calc_anom_ndvi_byilon.R")
source("R/get_iinst.R")
```

## Rationale

This is to investigate the (causal?) relationships between the cumulative water deficit extremes (CWD) and NDVI extremes. We hypothesize that plants are adapted to the CWD climatology where they grow. This should imply that extreme negative NDVI anomalies occur at different levels of CWD across climatic gradients, but at similar levels in terms of the CWD return periods ($T_\text{CWDX}$).

## Looking at a known NDVI extreme

Based on Zscheischler et al., we take a point in northern France around:

```{r}
lon <- 50.0
lat <- 55

## Find longitude index of 0.05 degree grid
lon_hires <- seq(-179.975, 179.975, by = 0.05)
ilon <- which.min(abs(lon - lon_hires))
ilon
```
Get data in usable format.
```{r}
df <- calc_anom_ndvi_byilon(ilon)

tmp <- df %>% 
  mutate(len = purrr::map(df_tseries, ~nrow(.))) %>% 
  dplyr::filter(len==15) %>% 
  ## get fit metric
  # slice(1:100) %>% 
  mutate(fit = purrr::map2(df_tseries, lat, ~metric_greenx(.x, .y))) %>% 
  dplyr::filter(!identical(fit, NA)) %>% 
  mutate(tmp = purrr::map(fit, "df_metrics")) %>% 
  mutate(cor = purrr::map_dbl(tmp, ~{dplyr::filter(., .metric == "cor") %>% pull(.estimate)})) %>% 
  mutate(cor_test = purrr::map_dbl(tmp, ~{dplyr::filter(., .metric == "cor_test") %>% pull(.estimate)}))


df %>% 
  unnest(df_tseries) %>% 
```

```{r}
df2 <- calc_anom_ndvi_byilon(ilon)

df2 <- df2 %>% 
  unnest(df_tseries)

hist(df2$cwd, xlim = c(0,1000), breaks = 50)
hist(df2$return_period, xlim = c(0,50), breaks = 50)
```

```{r pressure}
gg1 <- df$df_tseries[[1]] %>% 
  ggplot() + 
  geom_line(aes(x = time, y = cwd), color = "tomato") +
  labs(title = "CWD")

gg2 <- df$df_tseries[[1]] %>% 
  ggplot() + 
  geom_line(aes(x = time, y = return_period), color = "royalblue") +
  labs(title = "CWD return period")

gg3 <- df$df_tseries[[1]] %>% 
  ggplot() + 
  geom_line(aes(x = time, y = zscore), color = "springgreen3") +
  labs(title = "NDVI anomaly")

gg1 /
  gg2 /
  gg3
```

```{r pressure}
df$df_tseries[[1]] %>% 
  ggplot(aes(x = cwd, y = ndvi_anom)) + 
  geom_point()

df$df_tseries[[1]] %>% 
  ggplot(aes(x = return_period, y = ndvi_anom)) + 
  geom_point()
```
